### 2011-01-26 paper/learningMethods.tex
Maded parameter table, fixed vector equation

 - amp - Amplitude       - allowable range
 - tau   - sine wave period   - allowable range
 - multIO - multiplier scaling inner joings from outer joints  - allowable range
 - multFB - multiplier scaling front joints from back joints  - allowable range
 - multLR - multiplier scaling left joints from right joints  - allowable range
(verify this)

\newcommand{\amp}{\mathrm{amp}}

Inuitively, SineModel5 starts with 8 identicaly sine waves of
amplitude $\amp$ and period $\tau$, multiplies the waves for all inner
motors by multIO, multiplies the waves for all front motors by multFB,
and multiplies the waves for all left motors by multLR.  To obtain the
actual motor position commands, these waves are offset by an
appropriate fixed constant so that the base position (when the sine
waves are at 0) is approximately a crouch (the position shown in
\figref{crouchingRobot}).  Finally, in this motion model, the ninth
"hip" motor is kept at a neutral position.  Thus, the commanded
position for all motors, as a vector function of time, is:

\begin{verbatim}
        [g_0(t) ]    [ \amp * sin(\tau t) ]
        [g_1(t) ]    [ \amp * sin(\tau t) ]
        [g_2(t) ]    [ \amp * sin(\tau t) ]
g(t)   [g_3(t) ] = [ \amp * sin(\tau t) ]
        [g_4(t) ]    [ \amp * sin(\tau t) ]
        [g_5(t) ]    [ \amp * sin(\tau t) ]
        [g_6(t..) ]    [ \amp * sin(\tau t) ]
\end{verbatim}

\edit{make figure to go here, show drawing with inner/outer, l/r, and f/b motors.}
\edit{JMC: Use photo of physical robot in this image, and add labels in photoshop?}
The nine subscripted functions correspond to the nine labeled motors in \figref{robotDiagram}

@@

Using the SineModel5 parametrized motion model described in the
previous section, along with the allowable ranges for each of the five
parameters (shown in \tabref{parameterTable}), the task becomes how to
choose the combination of five parameters that results in the fastest
motion, per the evaluation methods in \secref{fitnessEvaluation}.

>>>>

%\newcommand{\amp}{\ensuremath{\mathrm{amp}}}
\newcommand{\amp}{\ensuremath{\alpha}}

\begin{table}[h]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameter    & Description               & Range \\
\hline
\hline
\amp         & Amplitude                 & [0, 400] \\
\hline
$\tau$       & Period                    & [.5, 8] \\
\hline
$m_O$        & Outer motor multiplier    & [-2, 2] \\
\hline
$m_F$        & Front motor multiplier    & [-1, 1] \\
\hline
$m_R$        & Right motor multiplier    & [-1, 1] \\
\hline
\end{tabular}
\caption{The parameters used for the \emph{SineModel5} motion model.}
\tablabel{parameters}
\end{center}
\end{table}

Intuitively, SineModel5 starts with 8 identically sine waves of
amplitude $\amp$ and period $\tau$, multiplies the waves for all inner
motors by multIO, multiplies the waves for all front motors by multFB,
and multiplies the waves for all left motors by multLR.  To obtain the
actual motor position commands, these waves are offset by
appropriate fixed constants so that the base position (when the sine
waves are at 0) is approximately a crouch (the position shown in
\figref{crouchingRobot}).  Finally, in this motion model, the ninth
"hip" motor is kept at a neutral position.  Thus, the commanded
position for all motors, as a vector function of time, is:

\[
\vec{g}(t) =
\left[ {\begin{array}{c@{ }l@{ }l}
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \           m_F            & + C_I \\ % 0
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O \cdot m_F            & + C_O \\ % 1
\amp \cdot \sin(2\pi t / \tau) & \                                  & + C_I \\ % 2
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O                      & + C_O \\ % 3
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \                     m_R  & + C_I \\ % 4
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O           \cdot m_R  & + C_O \\ % 5
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \           m_F \cdot m_R  & + C_I \\ % 6
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O \cdot m_F \cdot m_R  & + C_O \\ % 7
0                              & \                                  & + C_C \\ % 8
\end{array} } \right]
\]

\noindent Here the fixed constants that determine the crouched
position are $C_I$ for inner motors, $C_O$ for outer motors, and $C_C$
for the center hip motor.

\edit{make figure to go here (or another section), show drawing with
  inner/outer, l/r, and f/b motors.}

The nine subscripted functions correspond to the nine labeled motors
in \figref{robotDiagram}

@@

Using the SineModel5 parametrized motion model described in the
previous section, along with the allowable ranges for each of the five
parameters (shown in \tabref{parameters}), the task becomes how to
choose the combination of five parameters that results in the fastest
motion, per the evaluation methods in \secref{fitnessEvaluation}.
